No Evidence for the Aquarius Co-Moving Group \\Resulting from a Disrupted Classical Globular Cluster\altaffilmark{1}

### 2013-01-29 2012-aqs/draft-aqs.tex
yolo

@@

\begin{abstract}
We present a detailed analysis of five Aquarius stream giant stars observed using the MIKE spectrograph on the Magellan Clay telescope.  Enhanced sodium and nickel abundances suggest the group is not the result of a dwarf satellite galaxy, and that its chemical enrichment environment is more like a globular cluster or the thick disk of the Milky Way. However, we find no evidence that the group is a result of a disrupted globular cluster. Our data indicate the Aquarius stream has a large metallicity dispersion of $\sigma(\mbox{[Fe/H}]) = 0.32$\,dex. No inverse Na-O correlation is present, and we find a positive Mg-Al relationship. Chemically, the group is indistinguishable from the Milky Way thick disk with the exception of one very interesting candidate, which is most likely tidal debris from $\omega$-Centurai. Assuming all other candidates are Aquarius members, we propose the co-moving group has arisen from a minor merger in the Milky Way's thick disk.

@@

\section{Introduction}
Galaxies are formed hierarchically through chaotic mergers of smaller systems. The Milky Way is no exception. In our own stellar halo, we see ongoing evidence of these accretion events. As accreting satellites infall onto the galaxy, tidal forces disrupt the dwarf, hurtling stars in leading and trailing directions. The phase space information of stars within these `stellar streams' are sensitive to the galactic potential. They can collectively constrain the fraction and distribution of accreted matter in the stellar halo, the sub-halo mass function, as well as the shape and extent of dark matter in the Milky Way. Moreover, individual chemical abundances can constrain the  precise nucleosynthesis sites where elements are forged, as well as trace the chemical evolution of the galaxy.

@@

Wide-field surveys have proved excellent sources for finding stellar streams. Dozens of streams reaching out up to 150\,kpc in the halo have been identified through photometric selections and matched-filtering techniques \citep{belokurov;et-al_2007,koposov_SG1}. Indeed, it is clear that a large fraction of the stellar halo has been built up by accretion. However, as \citet{helmi;white_1999} point out, these observing strategies are only successful for identifying streams that are sufficiently distant from the solar neighbourhood. A nearby stream, within $\sim$10\,kpc, will not appear as an over-density, as the stars would be sparsely positioned across the sky. Such substructures would only be detectable by their kinematics, or perhaps precise chemical abundances through a `chemical tagging' approach (e.g. see \citet{freeman;bland-hawthorn_2003}).

% Talk about RAVE
It is therefore necessary to survey solar neighbourhood stars with spectroscopy in order to detect any nearby substructures. The RAVE (Radial Velocity Experiment) team began such a survey in 2003 and have observed spectra from over 500,000 stars across 17,000 deg$^{2}$. As the name suggests, the primary goal of RAVE was to obtain radial velocities for the solar neighbourhood and beyond. In an attempt to remain kinematically unbiased, RAVE candidates were selected based only on their apparent magnitude. With the exception of bulge stars, where some photometric cuts were employed, all stars between 9 $<$ I $<$ 13 were observed. Almost all of these candidates have published radial velocity measurements \citep{steinmetz;et-al_2006}, and for a subset of stars with sufficient S/N, estimates of stellar parameters have been derived using a $\chi^2$ minimization technique \citep{zwitter;et-al_2008, siebert;et-al_2011}.

% Identification of the aquarius stream
Using these data, \citet{williams;et-al_2011} identified a co-moving group of nearby ($0.5\,\mbox{kpc} \lesssim d \lesssim 10\,\mbox{kpc}$) stars in the vicinity of the Aquarius constellation $(l, b) = (60\,^\circ, -55\,^\circ)$. Thus, the co-moving group was named the Aquarius stream. The stream is most apparent when examining velocities against galactic latitude for stars within $-70\,^\circ < b < -50\,^\circ$. \citet{williams;et-al_2011} employed a selection criteria of $-250\,\mbox{km s}^{-1} < V_{HEL} < -150\,\mbox{km s}^{-1}$, $30\,^\circ < l < 75\,^\circ$ and $J > 10.3$ to maximize the contrast between the stream and background, identifying 15 candidates in the process. The average heliocentric velocity of these members was found to be $V_{HEL} = -199\,\mbox{km s}^{-1}$, with a dispersion of 27\,km s$^{-1}$. The radial velocity uncertainties provided by the RAVE catalog are described to be $\sim$2\,km s$^{-1}$, so the wide kinematic distribution appears to be real.

% QUANTIFYING THE STREAM DETECTION
Upon examining the galactic longitude and velocities of Aquarius stars, the stream appears quite distinct from the halo. In order to quantify the statistical likelihood that the Aquarius stream is truly separate from a smooth halo distribution, \citet{williams;et-al_2011} compared the number of observed RAVE stars within $-70\,^\circ < b < -50\,^\circ$ against the Galaxia \citep{sharma;et-al_2011} and Besan\c{c}on \citep{robin;et-al_2003} galaxy simulations. The predicted particles in each model between $-70\,^\circ < b < -50\,^\circ$ were binned in $\Delta{l} \times \Delta{V_{hel}}$ blocks using varying grid cell sizes between $25\,^\circ$ to $70\,^\circ$ and $20\,\mbox{km s}^{-1}$ to $100\,\mbox{km s}^{-1}$ respectively. The RAVE sample was binned in the same way, and the statistical significance of the over-density is calculated for each cell. \citet{williams;et-al_2011} found the stream to be statistically significant ($>$4-$\sigma$) in 96\% of the grid cell sizes employed for the Besan\c{c}on model. By sampling the Galaxia model repeatedly with varying extinction rates, a similar result was found: between $75\pm15$\,\% to $80\pm18$\,\% of grid cells showed the Aquarius stream to significant at the 4-$\sigma$ level or higher. Given the high-latitude and proximity of the stream, it is not surprising that dust had a negligible effect on the statistical significance. \citet{williams;et-al_2011} concluded that the over-density in $l, V_{hel}$ is a true substructure, and neither the choice of galaxy model, cell size, nor the extinction model made any real difference to the stream detection significance.

@@

Given the extent of stellar debris the Sagittarius dwarf has littered throughout the Milky Way, it is reasonable to suspect the Aquarius stream might originate from the Sagittarius dwarf. Indeed, the Aquarius stream stars do not lie far from the orbital plane of Sagittarius and the metallicities reported by \citet{williams;et-al_2011} are not dissimilar from the Sagittarius stream. However, \citet{williams;et-al_2011} found the Aquarius space positions and kinematics (specifically $V_{Z}$ and $V_\phi$) are quite distinct from Sagittarius. Based on the phase space information available, \citet{williams;et-al_2011} concluded that the newly discovered stream could not be positively associated with the Monoceros stream, Hercules-Aquila cloud, or either the Canis Major or Virgo over-densities.

The Aquarius stream has a metallicity of $\mbox{[Fe/H]} \sim -1.0$, slightly more metal-rich than halo stars at the same distance. \citet{williams;et-al_2011} found the stream to have an average of $\mbox{[M/H]} = -1.0 \pm 0.4$, compared to $\mbox{[M/H]} = -1.1 \pm 0.6$ for background stars after the same selection cuts had been employed. Of the 12 Aquarius stars in the \citet{williams;et-al_2011} discovery sample with stellar parameters, the metallicity range is wide: between --2.02 and --0.33 dex. Spectroscopic observations of high resolution with high signal-to-noise ($S/N$) are necessary to accurately characterize the stream's metallicity distribution.

To this end, \citet{wylie-de-boer;et-al_2012} obtained high-resolution ($\mathcal{R} = 25,000$) spectra with modest $S/N$ ($\sim$30 pixel$^{-1}$) for six Aquarius stream stars. Their data indicate a very narrow metallicity distribution: $\mbox{[Fe/H]} = -1.09 \pm 0.10$\,dex extending between $\mbox{[Fe/H]} = -1.25$ to $-0.98$\,dex. The largest [Fe/H] discrepancy between the \citet{williams;et-al_2011} and \citet{wylie-de-boer;et-al_2012} study was $\Delta\mbox{[Fe/H]} = -0.66$\,dex for the most metal-rich star in the \citet{williams;et-al_2011} sample. The most metal-poor star in the \citet{williams;et-al_2011} study was not observed by \citet{wylie-de-boer;et-al_2012}. 
In addition to ascertaining stellar parameters, \citet{wylie-de-boer;et-al_2012} measured elemental abundances for the Aquarius stream stars -- the only study to do so until now. Their study primarily focussed on light elements: Na, O, Ni, Mg, and Al. Chemical patterns in these light elements arise as natural consequences of nucleosynthetic processes in massive stars. These patterns have been repeatedly observed in globular clusters. Specifically, an anti-correlation between sodium and oxygen abundance has been found to be ubiquitous to globular clusters. Originally this was thought to arise from internal mixing along the giant branch. However, dwarf stars were later found to exhibit strong Na-enhancement and O-depletions, contrary to what would be expected if the Na-O anti-correlation was purely a result of internal mixing. It is well known now that photospheric abundance variations resulting from internal mixing are limited to C, N and Li. While the exact astrophysical mechanism for oxygen-depletion remains under debate, the chemical relationship is well-established empirically. The Na-O pattern provides the best chemical evidence that their chemical enrichment history has been dominated by Sn \textsc{ii} events and that those stars formed in a globular cluster-like environment.

From high-resolution spectroscopy of five stars in Aquarius, four of which had Na and O measurements, \citet{wylie-de-boer;et-al_2012} found two stars with super-solar sodium; slightly higher [Na/Fe] ratios than halo stars of the same metallicity. However, no strong oxygen depletion was evident in their data.

There are other chemical abundance patterns that allow us to infer the chemical evolution of a given cluster. \citet{nissen;schuster_1997} first noted that distant solar neighbourhood stars were enriched in [Ni/Fe] and [Na/Fe]. \citet{fulbright_2000} came to a similar conclusion: only somewhat distant ($R_\odot > 20$\,kpc) stars are likely to be sodium deficient. If the stellar halo has been built up from the accretion of smaller dwarf satellites, \citet{nissen;schuster_1997} proposed that this chemical trend may be indicative of the halo merger history since stars at larger $R_\odot$ are more likely to have been accreted rather than formed in-situ. \citet{wylie-de-boer;et-al_2012} found all the Aquarius stars in their sample to be enriched in both sodium and nickel; contrary to what would be expected if the stars originated from a disrupted dSph satellite. This provided an additional indication that the Aquarius stream stars originated in a globular cluster-like environment.

Combined with the low level of chemical scatter present in their sample, these chemical indicators led \citet{wylie-de-boer;et-al_2012} to conclude that the Aquarius stream must be the result of a tidally disrupted globular cluster. \citet{williams;et-al_2011} had previously precluded this possibility with any known globular clusters after modelling an Aquarius-like progenitor infalling onto the Milky Way and comparing the predicted $l, b, V_{hel}$ with known, nearby globular clusters of similar metallicities. No known globular cluster could match their simulation.

We seek to investigate the nature of the Aquarius stream, specifically the recent globular cluster origin claim made by \citet{wylie-de-boer;et-al_2012}. We present a detailed analysis for five  Aquarius stream members from high-resolution, high $S/N$ observations taken using the Magellan Inamori Kyocera Echelle spectrograph \citep{bernstein;et-al_2003} on the Magellan Clay telescope. Details of the observations and data reduction are outlined in the following section. The data analysis is chronicalled in Section \ref{sec:analysis} and a detailed discussion of these results resides in Section \ref{sec:discussion}. In Section \ref{sec:conclusion} we present our conclusions and critical interpretations.

\begin{deluxetable*}{lcccccccccc}
\tablecolumns{1}
\tabletypesize{\scriptsize}
\tablecaption{Observations\label{tab:observations}}
\tablehead{
	\colhead{Designation} &
	\colhead{$\alpha$} &
	\colhead{$\delta$} &
	\colhead{Observed} &
	\colhead{Airmass} &
	\colhead{Seeing} &
	\colhead{$t_{exp}$} &
	\colhead{S/N\tablenotemark{a}} &
	\colhead{$V_{rad}$} &
	\colhead{$V_{hel}$} &
	\colhead{$V_{err}$} \\
 & (J2000) & (J2000) & Date & & (") & (secs) & (px$^{-1}$) & (km s$^{-1}$) & (km s$^{-1}$) & (km s$^{-1}$)
}
\startdata

@@

The most complete sample of Aquarius stream stars is presented in the discovery paper of \citet{williams;et-al_2011}. Our sample includes five stars: four common to the \citet{wylie-de-boer;et-al_2012} study, and an additional star from the original \citet{williams;et-al_2011} sample. The additional candidate, J2306265-085103, was observed by the RAVE survey but had a $S/N$ ratio too low for stellar parameters to be accurately determined. All program stars were observed in July 2011 in good seeing at low airmass (Table \ref{tab:observations}), and X additional standard stars were observed in March 2011. All observations were taken using a 1.0'' slit, providing a spectral resolution of $\mathcal{R} = 28,000$ in the blue and $\mathcal{R} = 22,000$ in the red arm. The total exposure times for our program stars varied per star from X-Y seconds to ensure a Signal-to-Noise ratio ($S/N$) ratio in excess of 100 per pixel element at 600 nm.

@@

Calibration frames were taken at the start of each night, including twenty flat-field frames (10 quartz, 10 milky) and 10 Th-Ar arc lamp exposures for wavelength calibration. The data were reduced using the CarPy pipeline\footnote{http://code.obs.carnegiescience.edu/mike}. One of our standard stars, HD 41667, was also reduced using standard extraction and calibration methods in \textsc{iraf}. The resultant spectra from both reduction approaches were compared for residual fringing, $S/N$, and wavelength calibration. No noteworthy differences were present, and the CarPy pipeline was utilized for the remainder of the reductions. Each reduced echelle order was carefully normalized using a third order spline with defined knot spacing. Normalized orders   were stitched together to provide a single one-dimensional spectrum from 3800-9400\,\AA{}.

The white dwarf HR 6141 was observed on X as a telluric standard. The $S/N$ ratio for HR 6141 exceeds that in any of our other standard or  program stars. Although the atmospheric conditions at Las Campanas Observatory are certain to change throughout the night and between observing runs, we are primarily using this spectra to identify lines that are affected by telluric absorption. Critical transitions necessary for abundance analyses that are affected by the earth's atmosphere are corrected for telluric absorption (see \S\ref{sec:telluric-absorption}).

@@

\subsection{Radial Velocities}
\label{sec:radial-velocities}
The radial velocity for each star was determined in a two-step method. An initial estimate of the radial velocity was ascertained by cross-correlation with a synthetic spectrum of a giant star with $T_{eff} = 4500$\,K, $\log{g} = 1.5$, and [M/H] $= -1.0$ across the wavelength range $8450 - 8700$ \AA{}. The observed spectrum was shifted to the pseudo-rest frame using this initial velocity estimate. Velocities found from cross-correlation are typically within 1\,km\,s$^{-1}$ of our final published value.

With our spectra at near-rest, we measured the equivalent widths of $\sim$200 lines by automatically fitting Gaussian functions to the absorption profiles (see Section \ref{sec:line-measurements}). Fitted Gaussian profiles provide us with a measured equivalent width, the full-width half-maximum and the central wavelength of the profile. Thus, the residual radial velocity can be found from the ratio of the central and rest wavelengths. The final radial velocity for the star is provided by the initial velocity and the mean of $\sim$200 residual line velocity measurements. Figure \ref{fig:line-velocities} shows the line velocities for HD 41667 after being placed at pseudo-rest using our cross-correlation velocity of 314.4\,km s$^{-1}$. As expected, the mean residual offset is small ($-0.75$\,km s$^{-1}$), and the standard deviation is 0.79\,km s$^{-1}$ from 164 line measurements. This provides us with a final measured radial velocity of $313.7 \pm 0.1$\,km s$^{-1}$. This process was performed for all observations. The radial velocities published in Table \ref{tab:observations} are the final values from this two-step method. Heliocentric velocities agree quite well with the \citet{williams;et-al_2011} published values: the mean offset is $\langle\Delta{V_{hel}}\rangle = 2.5 \pm 2.7$\,km\,s$^{-1}$, demonstrating the accuracy of the velocities published in the RAVE catalog.

\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/line-velocity.pdf}
	\caption{Residual velocities for each absorption line with a well-fitted Gaussian profile after correcting for  doppler shift with our initial cross-correlation measurement. The mean residual velocity $-0.75$\,km\,s$^{-1}$ is within the 1-$\sigma$ cross-correlation uncertainty of $\pm0.9$\,km\,s$^{-1}$.}
	\label{fig:line-velocities}
\end{figure}

@@

The equivalent widths for all absorption lines were measured automatically using software written for this study. Given the rest wavelength and an initial guess of the full-width half-maxium (FWHM), a Gaussian function is iteratively fitted to the absorption profile. At the same time, the local continuum is found within 20\,\AA{} either side of the rest wavelength using a second-order polynomial. Measuring the local continuum ensures any errors in our initial normalisation or order-stitching do not propagate through to our equivalent width measurements. When determining the local continuum, any neighbouring group of pixels that deviate significantly ($>$2-$\sigma$) from the local continua either belong to a persistent cosmic ray hit, or they are trough points of a neighbouring absorption profile. We attempt to fit a Gaussian profile to each group of deviating pixels, using the current best estimate for the local continuum. If a Gaussian profile is successfully fitted to the deviating group and its surrounding pixels, we assume the outlier points belong to an absorption profile and all points belonging to that profile are excluded from the continuum determination.

>>>>

% TODO:
% [DONE] Na/O subplots
% Na/O comparison with halo
% [DONE] Mg/Al subplots
% - Ni/Na plane plot
% - Add standard stars to observations table
% - Add standard stars chemical abundances
% - Add in-line text referencing standard star chemical abundances
% - Uncertainties analysis
% - Strontium?
% - Carbon?
% - Distance calculations
% - Transverse motions table
% - Transverse motions text
% - Orbital energies plot
% - Minor merger text
% - Conclusions

% Casey, Keller, Alves-Brito, Frebel, Da Costa, Schlaufman, Freeman, Heather, QinQin

@@

\begin{abstract}
We present a detailed analysis of five Aquarius stream candidate stars observed using the MIKE spectrograph with the Magellan Clay telescope.  Enhanced [Na/Fe] and [Ni/Fe] abundance ratios suggest the co-moving group is not the result of a dwarf satellite galaxy, and that its chemical enrichment environment is more representative of either a globular cluster, or the Milky Way thick disc. However, we find no evidence that the stream is a result of a disrupted cluster. Our data indicate the Aquarius stream has a  metallicity dispersion of $\sigma(\mbox{[Fe/H}]) = 0.32$\,dex. No inverse Na-O correlation is present, and we find a positive Mg-Al relationship. Chemically, the group is indistinguishable from the Milky Way thick disk with the exception of one very interesting candidate, which we hypothesise is tidal debris from $\omega$-Centurai. Assuming all other candidates are Aquarius members, we propose the co-moving group has arisen from a minor merger in the Milky Way's thick disk.

@@

\section{Introduction}
Galaxies are hierarchically formed through chaotic mergers of smaller systems. The Milky Way is no exception. The accumulating stellar debris in our own galactic halo provides ongoing evidence for such merging events. As accreting satellites infall onto the galaxy, tidal forces disrupt the dwarf, hurtling stars in leading and trailing directions. Unsurprisingly, the velocities of stars within these `stellar streams' are sensitive to the galactic potential. As such, their phase-space information can collectively constrain the fraction and distribution of accreted matter in the galaxy, the sub-halo mass function, as well as the shape and extent of dark matter in the Milky Way. Moreover, individual chemical abundances can constrain the  precise nucleosynthesis sites where elements are forged, as well as trace the chemical evolution of the galaxy.

@@

Wide-field surveys have proved excellent sources for finding stellar streams. Dozens have been identified through photometric selections and metched-filtering techniques, with some to a galactocentric distance of 100\,kpc \citep{belokurov;et-al_2007,koposov_SG1, drake;et-al_2013}. Indeed, it is clear that a large fraction of the stellar halo has been built up by accretion. However, as \citet{helmi;white_1999} point out, these observing strategies are only successful for identifying streams that are sufficiently distant from the solar neighbourhood. A nearby stream, within $\sim$10\,kpc, will not appear as an over-density, as the stars would be sparsely positioned across the sky. Such substructures would only be detectable by their kinematics, or perhaps precise chemical abundances through a `chemical tagging' approach (e.g. see \citet{freeman;bland-hawthorn_2003}).

% Talk about RAVE
It is therefore necessary to survey solar neighbourhood stars with spectroscopy to permit any nearby substructures to reveal themselves. The RAVE (Radial Velocity Experiment) team began such a survey in 2003 and have observed spectra from over 500,000 stars across 17,000\,deg$^{2}$. As the name hints, the primary goal of RAVE was to obtain radial velocities for the solar neighbourhood and beyond. In an attempt to remain kinematically unbiased, RAVE candidates were selected based only on their apparent magnitude. With the exception of bulge stars, where some photometric cuts were employed, all stars between 9 $<$ I $<$ 13 were observed. Almost all of these candidates have published radial velocity measurements \citep{steinmetz;et-al_2006}, and for a subset of stars with sufficient Signal-to-Noise ($S/N$), estimates of stellar parameters have been derived using a $\chi^2$ minimization technique \citep{zwitter;et-al_2008, siebert;et-al_2011}.

% Identification of the aquarius stream
Using these data, \citet{williams;et-al_2011} identified a co-moving group of nearby ($0.5\,\mbox{kpc} \lesssim d \lesssim 10\,\mbox{kpc}$) stars in the vicinity of the Aquarius constellation $(l, b) = (60\,^\circ, -55\,^\circ)$. Thus, the co-moving group was named the Aquarius stream. The artefact is most apparent when examining velocities against galactic latitude for stars within $-70\,^\circ < b < -50\,^\circ$. \citet{williams;et-al_2011} employed a selection criteria of $-250\,\mbox{km s}^{-1} < V_{\rm hel} < -150\,\mbox{km s}^{-1}$, $30\,^\circ < l < 75\,^\circ$ and $J > 10.3$ to maximize the contrast between the stream and background, identifying 15 candidates in the process. The average heliocentric velocity of these members was found to be $V_{\rm hel} = -199\,\mbox{km s}^{-1}$, with a dispersion of 27\,km s$^{-1}$. The radial velocity uncertainties provided by the RAVE catalog are described to be $\sim$2\,km s$^{-1}$, so the wide kinematic distribution appears to be real.

% QUANTIFYING THE STREAM DETECTION
Upon examining the galactic longitude and velocities of Aquarius stars, the stream appears quite distinct from the halo. In order to quantify the statistical likelihood that the Aquarius stream is truly separate from a smooth halo distribution, \citet{williams;et-al_2011} compared the number of observed RAVE stars within $-70\,^\circ < b < -50\,^\circ$ against the Galaxia \citep{sharma;et-al_2011} and Besan\c{c}on \citep{robin;et-al_2003} galaxy simulations. The predicted particles in each model between $-70\,^\circ < b < -50\,^\circ$ were binned in $\Delta{l} \times \Delta{V_{\rm hel}}$ blocks using varying grid cell sizes between $25\,^\circ$ to $70\,^\circ$ and $20\,\mbox{km s}^{-1}$ to $100\,\mbox{km s}^{-1}$. The RAVE sample was binned in the same way, and the statistical significance of the observed over-density is discretized. \citet{williams;et-al_2011} found the stream to be statistically significant ($>$4-$\sigma$) in 96\% of the cell proportions employed for the Besan\c{c}on model. By sampling the Galaxia model repeatedly with varying extinction rates, a similar result was found: between $75\pm15$\,\% to $80\pm18$\,\% of grid cells showed the Aquarius stream to significant at the 4-$\sigma$ level or higher. Given the high-latitude and proximity of the stream, it is not surprising that dust had a negligible effect on the statistical significance. \citet{williams;et-al_2011} concluded that the over-density in $l, V_{\rm hel}$ is a true substructure, and neither the choice of galaxy model, cell dimension, nor the extinction model made any real difference to the detection significance.

@@

The Sagittarius stream is arguably the most prominent ongoing accretion event in the galaxy. Given the extent of stellar debris the dwarf has littered throughout the Milky Way, it is reasonable to suspect the Aquarius stream might originate from the Sagittarius dwarf. Indeed, the Aquarius  stars do not lie far from the orbital plane of Sagittarius, and the metallicities reported by \citet{williams;et-al_2011} are not dissimilar from the Sagittarius stream. However, \citet{williams;et-al_2011} found the Aquarius transverse motions (specifically $V_{Z}$ and $V_\phi$) to be quite distinct from Sagittarius. Based on the phase space information available, \citet{williams;et-al_2011} concluded that the newly discovered stream could not be positively associated with the Monoceros stream, Hercules-Aquila cloud, or either the Canis Major or Virgo over-densities.

The Aquarius stream has a metallicity of $\mbox{[Fe/H]} \sim -1.0$, slightly more metal-rich than halo stars at the same distance. \citet{williams;et-al_2011} found the stream to have an average of $\mbox{[M/H]} = -1.0 \pm 0.4$, compared to $\mbox{[M/H]} = -1.1 \pm 0.6$ for background stars after the same selection cuts had been employed. Of the 12 Aquarius stars in the \citet{williams;et-al_2011} discovery sample with stellar parameters, the metallicity range is wide: between --2.02 and --0.33 dex. Spectroscopic observations of high resolution with high $S/N$ are necessary to accurately characterize the stream's metallicity distribution.

To this end, \citet{wylie-de-boer;et-al_2012} obtained high-resolution ($\mathcal{R} = 25,000$) spectra with modest $S/N$ ($\sim$30 pixel$^{-1}$) for six Aquarius stream stars. Their data indicate a very narrow metallicity distribution: $\mbox{[Fe/H]} = -1.09 \pm 0.10$\,dex extending between $\mbox{[Fe/H]} = -1.25$ to $-0.98$\,dex. Observations of such minimal chemical scatter from stars with a common origin is typically noted in either globular, or open clusters. The largest [Fe/H] discrepancy between the \citet{williams;et-al_2011} and \citet{wylie-de-boer;et-al_2012} study was $\Delta\mbox{[Fe/H]} = -0.66$\,dex for the most metal-rich star in the \citet{williams;et-al_2011} sample. The most metal-poor star in the \citet{williams;et-al_2011} study was not observed by \citet{wylie-de-boer;et-al_2012}.

In addition to ascertaining stellar parameters, \citet{wylie-de-boer;et-al_2012} measured elemental abundances for the Aquarius stream stars -- the only study to do so until now. The authors primarily focussed on light elements: Na, O, Ni, Mg, and Al. Chemical patterns in these light elements arise as natural consequences of nucleosynthetic processes in massive stars. These patterns have been repeatedly observed in globular clusters. Specifically, an anti-correlation between sodium and oxygen content appears ubiquitous to globular clusters. Originally this relationship was thought to arise from internal mixing along the giant branch. However, dwarf globular cluster stars were found to exhibit strong Na-enhancement and O-depletion, contrary to what would be expected if the Na-O anti-correlation was purely a result of internal mixing. It is well known now that photospheric abundance variations resulting from internal mixing are limited to carbon, nitrogen and lithium. Additionally, light element variations can be explained by classic nucleosynthetic pathways, albeit extreme temperatures are necessary for such relationships to arise \--- much higher than would reasonably be expected in globular cluster stars. Several descriptions for an astrophysical site that would permit such nucleosynthetic processes have been hypothesized, including massive intermediate-mass Asymptotic Giant Branch (AGB) binary stars \citep{de_mink;et-al_2009} and fast-rotating massive stars \citep{decressin;et-al_2007}. While the exact formation site is still under debate, the chemical relationship is well-established empirically. The Na-O pattern provides the best chemical evidence that their chemical enrichment history has been dominated by Sn \textsc{ii} events and that those stars formed in a globular cluster-like environment.

From high-resolution spectroscopy of five candidate Aquarius stars, four of which had sodium and oxygen abundance measurements, \citet{wylie-de-boer;et-al_2012} found two stars with super-solar sodium; slightly higher [Na/Fe] ratios than halo stars of the same metallicity. However, no strong oxygen depletion was evident in the data. Thus, they observed no evidence of a classical Na-O inverse correlation in the Aquarius stream.

There are other chemical abundance patterns that allow us to infer the chemical enrichment environment. \citet{nissen;schuster_1997} first noted that nearby solar neighbourhood stars were enriched in [Ni/Fe] and [Na/Fe]. \citet{fulbright_2000} came to a similar conclusion: only somewhat distant ($R_\odot > 20$\,kpc) stars are likely to be sodium deficient. If the stellar halo has been built up from the accretion of smaller dwarf satellites, \citet{nissen;schuster_1997} proposed that this chemical trend may be indicative of the halo merger history since stars at larger $R_\odot$ are more likely to have been accreted rather than formed in-situ. \citet{wylie-de-boer;et-al_2012} found all the Aquarius stars in their sample to be enriched in both sodium and nickel; contrary to what would be expected if the stars originated from a disrupted dwarf spheroidal (dSph) galaxy. This provided an additional indication that the Aquarius stream stars originated in a globular cluster-like environment.

Combined with the low level of chemical scatter present in their sample, these chemical indicators led \citet{wylie-de-boer;et-al_2012} to conclude that the Aquarius stream is the result of a tidally disrupted globular cluster. \citet{williams;et-al_2011} had previously precluded this possibility with any known globular clusters after modelling an Aquarius-like progenitor infalling onto the Milky Way and comparing the predicted $l, b, V_{\rm hel}$ with known, nearby globular clusters of similar metallicities. No known globular cluster could match their simulation. If both scenarios are accurate then the undiscovered disrupting cluster might still remain, and would be relatively close by.

We seek to investigate the nature of the Aquarius stream, specifically the recent globular cluster origin claim made by \citet{wylie-de-boer;et-al_2012}. We present a detailed analysis for five Aquarius stream candidates from high-resolution, high $S/N$ observations taken using the Magellan Inamori Kyocera Echelle spectrograph \citep{bernstein;et-al_2003} with the Magellan Clay telescope. Details of the observations and data reduction are outlined in the following section. The data analysis is chronicled in Section \ref{sec:analysis} and a detailed discussion of these results resides in Section \ref{sec:discussion}. In Section \ref{sec:conclusion} we present our conclusions and critical interpretations.

\begin{deluxetable*}{lcccccccccc}
\tablecolumns{1}
\tabletypesize{\scriptsize}
\tablecaption{Observations\label{tab:observations}}
\tablehead{
	\colhead{Designation} &
	\colhead{$\alpha$} &
	\colhead{$\delta$} &
	\colhead{Observed} &
	\colhead{Airmass} &
	\colhead{Seeing} &
	\colhead{$t_{exp}$} &
	\colhead{S/N\tablenotemark{a}} &
	\colhead{$V_{\rm rad}$} &
	\colhead{$V_{\rm hel}$} &
	\colhead{$V_{\rm err}$} \\
 & (J2000) & (J2000) & Date & & (") & (secs) & (px$^{-1}$) & (km s$^{-1}$) & (km s$^{-1}$) & (km s$^{-1}$)
}
\startdata

@@

The most complete sample of Aquarius stream stars is presented in the discovery paper of \citet{williams;et-al_2011}. Our sample includes five stars: four common to the \citet{wylie-de-boer;et-al_2012} study, and an additional candidate from the original \citet{williams;et-al_2011} sample. The supplementary star, J2306265-085103, was observed by the RAVE survey but had a $S/N$ ratio too low for stellar parameters to be accurately determined. All program stars were observed in July 2011 in good seeing at low airmass (Table \ref{tab:observations}), and X additional standard stars were observed in March 2011. All observations were taken using a 1.0'' slit, providing a spectral resolution of $\mathcal{R} = 28,000$ in the blue and $\mathcal{R} = 22,000$ in the red arm. The total exposure times for our program stars varied per star from X-Y seconds to ensure a $S/N$ ratio in excess of 100\,pixel$^{-1}$ at 600\,nm.

@@

Calibration frames were taken at the start of each night, including twenty flat-field frames (10 quartz, 10 milky) and 10 Th-Ar arc lamp exposures for wavelength calibration. The data were reduced using the CarPy pipeline\footnote{http://code.obs.carnegiescience.edu/mike}. One standard stars, HD 41667, was also reduced using standard extraction and calibration methods in \textsc{iraf}. The resultant spectra from both approaches were compared for residual fringing, $S/N$, and wavelength calibration. No noteworthy differences were present, and the CarPy pipeline was utilized for the remainder of the data reductions. Each reduced echelle order was carefully normalized using a third order spline with defined knot spacing. Normalized orders were stitched together to provide a single one-dimensional spectrum from 3800-9400\,\AA{}.

The white dwarf HR 6141 was observed on X as a telluric standard. The $S/N$ ratio for HR 6141 exceeds that in any of our standard or program stars. Although the atmospheric conditions at Las Campanas Observatory are certain to change throughout the night and between observing runs, we are primarily using this spectra to identify lines that are affected by telluric absorption. Critical transitions necessary for abundance analyses that are affected by the earth's atmosphere are corrected for telluric absorption (see \S\ref{sec:telluric-absorption}).

@@

\subsection{Radial Velocities}
\label{sec:radial-velocities}
The radial velocity for each star was determined in a two-step method. An initial estimate of the radial velocity was ascertained by cross-correlation with a synthetic spectrum of a giant star with $T_{\rm eff} = 4500$\,K, $\log{g} = 1.5$, and [M/H] $= -1.0$ across the wavelength range $8450 - 8700$ \AA{}. The observed spectrum was shifted to the pseudo-rest frame using this initial velocity estimate. Velocities found from cross-correlation are typically within 1\,km\,s$^{-1}$ of our final published value.

With our spectra at near-rest, we measured the equivalent widths of $\sim$200 lines by automatically fitting Gaussian functions to the absorption profiles (see Section \ref{sec:line-measurements}). Fitted Gaussian profiles provide us with a measured equivalent width, the full-width half-maximum (FWHM) and the central wavelength of the profile. Thus, the residual radial velocity can be found from the ratio of the central and rest wavelengths. The final radial velocity for the star is provided by the initial velocity and the mean of $\sim$200 residual line velocity measurements. Figure \ref{fig:line-velocities} shows the line velocities for HD 41667 after being placed at pseudo-rest using our cross-correlation velocity of 314.4\,km s$^{-1}$. As expected, the mean residual offset is small ($-0.75$\,km s$^{-1}$), and the standard deviation is 0.79\,km s$^{-1}$ from 164 line measurements. This provides us with a final measured radial velocity of $313.7 \pm 0.1$\,km s$^{-1}$. This process was performed for all observations. The radial velocities published in Table \ref{tab:observations} are the final values from this two-step method. Heliocentric velocities agree quite well with those compiled by \citet{williams;et-al_2011} from the RAVE survey: the mean offset is $\langle\Delta{V_{\rm hel}}\rangle = 2.5 \pm 2.7$\,km\,s$^{-1}$, demonstrating the accuracy of the velocities published in the RAVE catalog.

\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/line-velocity.pdf}
	\caption{Residual velocities for each absorption line with a well-fitted Gaussian profile after correcting for doppler shift using the initial cross-correlation measurement. The mean residual velocity $-0.75$\,km\,s$^{-1}$ is within the 1-$\sigma$ cross-correlation uncertainty of $\pm0.9$\,km\,s$^{-1}$.}
	\label{fig:line-velocities}
\end{figure}

@@

The equivalent widths for all absorption lines were measured automatically using software written for this study. Given the rest wavelength and an initial guess of the FWHM, a Gaussian profile is iteratively fitted to the absorption line. At the same time, the local continuum is found within 20\,\AA{} either side of the rest wavelength using a second-order polynomial. Measuring the local continuum ensures any errors in our initial normalisation or order-stitching do not propagate through to our equivalent width measurements. When determining the local continuum, any neighbouring group of pixels that deviate significantly ($>$2-$\sigma$) from the local continua either belong to a persistent cosmic ray hit, or they are trough points of a neighbouring absorption profile. We attempt to fit a Gaussian profile to each group of deviating pixels, using the current best estimate for the local continuum. If a Gaussian profile is successfully fitted to the deviating group and its surrounding pixels, we assume the outlier points belong to an absorption line and all pixels belonging to that profile are excluded from the continuum determination.

When fitting Gaussian profiles, the $\chi^2$ difference between the observed spectra and the fitted function is minimized. In order to account for crowded absorption regions, where the $\chi^2$ value might be influenced by a nearby or blended profile, our $\chi^2$ function is weighted based on the distance to the rest wavelength by the function
